---
title: "Falsified Interviews"
author: "Kevin Glock"
date: "30 03 2021"
output:
  html_document:
    highlight: textmate
  toc_depth: 2
  number_sections: yes
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
    echo = TRUE,
      include = TRUE,
    eval = TRUE,
  message = FALSE,
    results = 'hide',
      tidy = TRUE,
    tidy.opts = list(
      width.cutoff=60
      )
    )

#eval whether to evaluate the chunk
#echo whether to echo source code
#results 'markup', 'asis', 'hold', 'hide'
#tidy whether to reformat R code
#cache whether to cache results
#g.width, g.height, out.width, out.height device and output size of gures
#include whether to include the chunk results in output
#child lenames of child documents
#engine language name (R, python, . . . )
```



# required libraries


These libraries are used for the analysis.

```{r packages}
library(foreign) # read.spss
library(dplyr) # using pipes
library(haven) # read_por
```



# load respondents data


Get the data on respondents.

```{r resp data}
resp <- read.spss(
  "D:/IntFabric/data/ESS1HU.sav", # please specify the directory
                  to.data.frame=T, 
                  use.value.labels = F
  ) # data on respondents

dim(resp) # 1685 entries and 566 variables
```



#load respondents data


Get the data on interviewers.

```{r int data}
int <- read_por(
  "D:/IntFabric/data/ESS1cfHU.por" # please specify the directory
  ) # data on interviewers

dim(int) # 2484 entries and 176 variables
```

# merge data

Get rid of not used variables and merge the sets to a new merged subset.

```{r}
data1 <- subset.data.frame(
  resp,
  select = -c(
    name,
      essround,
        edition,
      proddate,
    cntry,
      pweight,
    pspwght,
      dweight,
        ctzship,
      cntbrth,
    lnghoma,
      lnghomb
    )
  ) # remove irrelevant and character variables

dim(data1) # 1685 entries and 554 variables

data2 <- subset.data.frame(
  int,
  select = c(
    IDNO,
      INTNUM1,
        INTNUM2,
      INTNUM3,
    TOTCINT1,
      TOTCINT2,
        TOTCINT3
    )
  ); dim(data2) # 2484 entries and 7 variables

mergeddata <- merge(
  data1,
  data2,
  by.x="idno",
  by.y = "IDNO",
  sort= T,
  no.dups = F
  )

mergeddata <- mergeddata %>%
  select(
    idno,
    INTNUM1,
    TOTCINT1,
    INTNUM2,
    TOTCINT2,
    INTNUM3,
    TOTCINT3,
    everything()
    ); dim(mergeddata) # 1685 entries and 560 variables

head(mergeddata, n=10)
```


# Methodological infos on dataset


Total non response rate.

```{r}
2484-1685 #=799

(799*100)/2484 #=32.17 %
1-0.3217 # 67.83 %
(1685/2484)*100 # 67.83%
```


How many interviewer?

```{r}
unique(int$INTNUM1) # 198 unique interviewer who started first contact (one NA)
unique(int$INTNUM2) # 19 (one NA)
unique(int$INTNUM3) # 2 (one NA)


sum(table(int$INTNUM1))
# 2461 first contacts
# 2484-2461=23 NAs

sum(table(int$INTNUM2)) # 35 re-issues
sum(table(int$INTNUM3)) # 4 re-issues

table(int$TOTCINT1)
table(int$TOTCINT2)
table(int$TOTCINT3)


# 436+224+124+45+7+2=838
# 436+224+124+45+937=1766

rm(list = c("resp", "int"))
```


How many total contacts being made by the interviews?

```{r}
data5.0 <- mergeddata %>% subset(mergeddata$TOTCINT1==0)
data5.1 <- mergeddata %>% subset(mergeddata$TOTCINT1==1)
data5.2 <- mergeddata %>% subset(mergeddata$TOTCINT1==2)
data5.3 <- mergeddata %>% subset(mergeddata$TOTCINT1==3)
data5.4 <- mergeddata %>% subset(mergeddata$TOTCINT1==4)
data5.5 <- mergeddata %>% subset(mergeddata$TOTCINT1==5)
data5.6 <- mergeddata %>% subset(mergeddata$TOTCINT1==6)
data5.7 <- mergeddata %>% subset(mergeddata$TOTCINT1==7)
data5.8 <- mergeddata %>% subset(mergeddata$TOTCINT1==8)
data5.9 <- mergeddata %>% subset(mergeddata$TOTCINT1==9)
data5.10 <- mergeddata %>% subset(mergeddata$TOTCINT1==10)

dim(data5.0) # 689 for all desired interviews resp. 513 for all performed interview
dim(data5.1) # 436 resp. 336
dim(data5.2) # 224 resp. 147
dim(data5.3) # 124 resp. 69
dim(data5.4) # 45 resp. 20
dim(data5.5) # 16 resp. 7
dim(data5.6) # 8 resp. 2
dim(data5.7) # 2 resp. 1
dim(data5.8) # 1 resp. 0
dim(data5.9) # 2 resp. 0
dim(data5.10)# 0 resp. 0

data5.0.1 <- mergeddata %>% subset(mergeddata$TOTCINT2==0)
data5.1.1 <- mergeddata %>% subset(mergeddata$TOTCINT2==1)
data5.2.1 <- mergeddata %>% subset(mergeddata$TOTCINT2==2)

dim(data5.0.1) # 7 resp. 7
dim(data5.1.1) # 4 resp. 4
dim(data5.2.1) # 0 resp. 0

data5.0.2 <- mergeddata %>% subset(mergeddata$TOTCINT3==0)
data5.1.2 <- mergeddata %>% subset(mergeddata$TOTCINT3==1)
data5.2.2 <- mergeddata %>% subset(mergeddata$TOTCINT3==2)

dim(data5.0.2) # 1 resp. 1
dim(data5.1.2) # 1 resp. 0
dim(data5.2.1) # 0 resp. 0

rm(list = c("data5.0", "data5.1", "data5.2", "data5.3", "data5.4", "data5.5", "data5.6", "data5.7", "data5.8", "data5.9", "data5.10", "data5.0.1", "data5.1.1", "data5.2.1", "data5.3.1", "data5.4.1", "data5.5.1", "data5.6.1", "data5.7.1", "data5.8.1", "data5.9.1", "data5.10.1", "data5.0.2", "data5.1.2", "data5.2.2"))
```


## methodological subset infos


How many interviewer?

```{r}
length(unique(mergeddata[,"INTNUM1"])) # 193 interviewers
unique(mergeddata[,"INTNUM2"]) # 15 interviewers (plus one NA)
unique(mergeddata[,"INTNUM3"]) # 0 interviewer (plus one NA)
# 193+15=208 interviewers
```

# variability approach


For the variability approach in the first step the variance for each interviewer and every question is calculated and summed up.
The difference between each observation for a question by interviewer and the mean of the question will provide a t-statistic which can be tested against a resampled distribution.

```{r}
dim(mergeddata)

anew <- subset.data.frame(mergeddata,
                          select = -c(3,5,7)) %>% 
  group_by(idno, INTNUM1) # sort it by interviewer one and match each interview

head(anew) 

anew[is.na(anew)] <-0 # All NAs should be 0 because of calculations

dim(anew)
head(anew) # Now the data is tidy; 1685 obs on 557 var
```


## calculate the means


Pay attention for 1685 entries, 557 total columns but idno and INTNUM1-3 should not be includes.

```{r}
bnew <- anew[,c(5:557)] %>% 
  colMeans() %>% 
  rbind.data.frame()

names(bnew) <- colnames(anew[5:557])

head(bnew) # now we have the mean values for every variable

bnew <- bnew[rep(
  seq_len(
    ncol(bnew)
    ), 
  each = 1685), ] # each must be adapted

head(bnew, n = 5)
tail(bnew, n = 5)

bnew <- bnew[-c(1686:nrow(bnew)), ] # make sure there are no redundant rows

nrow(bnew) # 1685

# now we have a df with all means for every variable for each observation
# we have to apply the calculation for each observation

head(anew)

cnew <- anew[,-(1:4)] # we have to remove idno and INTNUM1-3 to make rowwise calculations in the next step

dim(cnew) # stated values for each interview; 1685 obs and 553 vars
dim(bnew) # mean for each question; 1685 obs and 553 vars

```


## calculate variabilities


Variability for each question over each interview

```{r}
calc <- (cnew-bnew)^2
head(calc)

calc2 <- cbind(
  anew[,c("idno","INTNUM1", "INTNUM2", "INTNUM3")], calc
  )

dim(calc2) # like before 1685 obs on 557 vars
head(calc2)
```
  

How many interviews per interviewer?

The calculation can be found in the xlsx table in the annex.

```{r}
sort(table(calc2[, 3])) # 25 interviews by IntNum 2
sort(table(calc2[, 4])) # 0 interviews by IntNum 3
sort(table(calc2[, 2])) # 1685-25 = 1660 interviews by IntNum 1
length(unique(calc2$INTNUM1))
length(unique(calc2$INTNUM2))
```


```{r}

calc3 <- calc2 %>% 
  group_by(INTNUM1, INTNUM2) %>% 
  summarise(.groups = "keep", 
            across(.cols = 5:554,
                   .fns = sum
                   )
            ) # sum up for each interviewer over all questions

rm(list = c("anew", "bnew", "cnew"))

dim(calc3) # 208 unique interviewer because of grouping by INTNUM1-2 and 552 vars
head(calc3)
```


## get the test statistic T


Get the test statistic T (total variability) for the clustered interviewer and for the whole survey.

```{r}
calc4 <- cbind.data.frame(
  calc3[c("INTNUM1", "INTNUM2")],
  rowsum = rowSums(calc3[3:552])
  ) # create a new object containing the INTNUMs and the total variability aggregated by INTNUMs

sort.calc4 <- calc4[order(calc4$rowsum) ,] # resort it by the rowsums to get ascending values of the variabilities

head(sort.calc4, n = 5) 

plot(density(calc4$rowsum)
     ); options(scipen=5) # the density of variability over all interviewers

sd(calc4$rowsum) # 119066901
mean(calc4$rowsum) # 176699764

# 176699764-119066901=57632863
# 176699764+119066901=295766665

sort(table(calc4$INTNUM1)
     ) # we can see that some are double or triple this is because they are re-issued by a second and third person
head(calc4, n = 20) # look on the entries 6 and 7 for example

length(which(sort.calc4$rowsum < 100000000)) # fifty-seven interviews show suspiciously low total variabilities at first sight

head(sort.calc4, n = 5) # lowest value 6044290 for interviewer 2086; keep in mind that this are aggregated values!
tail(sort.calc4, n = 5) # highest value 599664843 for interviewer 6049
```


## whole dataset


Get independent variabilities for the interviews.

```{r}
calc5 <- cbind(
  calc2[c("idno", "INTNUM1")], calc
  ); head(calc5, n = 5)

calc6 <- cbind.data.frame(
  calc5[c("idno", "INTNUM1")], 
  rowsum=rowSums(calc5[3:554])
  ); head(calc6, n = 5)

plot(density(calc6$rowsum)
     ) # density plot for unique interviews not grouped by interviewers

sd(calc6$rowsum) # 15601634
mean(calc6$rowsum) #21812202

sort.calc6 <- calc6[order(calc6$rowsum) ,] # now sorted by rowsums not by respondends ID

head(sort.calc6, n = 5) # lowest value 2352503 for interview 2308; keep in mind that this are seperated interview values not aggregated
tail(sort.calc6, n = 5) # highest value 104602583 for interview 2089

write.csv2(calc6, "data.csv")
getwd()
```


# resampling


Resample from the subset and check of plausibility.

```{r}
N <- 100000; SP <- sample(calc4$rowsum,
                          N, 
                          replace=T
                          ) # draw a sample of size N=100,000 from the aggregated rowsums

sd(SP) # 119385175
mean(SP) # 177189578
# 177189578-119385175=57804403
# 177189578+119385175=296574753

mean(calc4$rowsum) # 176699764
sd(calc4$rowsum) # 119066901
# 176699764-119066901=57632863
# 176699764+119066901=295766665

plot(density(SP),
     col ="grey",
     main = "Plausibilit채t",
     xlab= "Totalvariabilit채t T in Interview-Clustern (gepunktet MW +/- St.Abw.)",
     lwd=2); lines(density(calc4$rowsum), 
                   col= "black",
                   lwd=2); abline(v= c(57804403, 177189578, 296574753),
                                  col="grey",
                                  lty="dotted",
                                  lwd=3); abline(v= c(57632863, 176699764, 295766665),
                                  col="black",
                                  lty="dotted",
                                  lwd=3); legend("topright", legend = c("SP", "Resample"),  fill = c("black", "grey"), bty = "n");
                                    options(scipen=5) # plot the density of the original rowsums and the resampled ones


```


Get the densities

```{r}
dat2 <- data.frame(V1 = calc4$rowsum)
round(
  sort(
    with(dat2, V1/sum(V1))
    ), digits = 6)

round(
  cumsum(
    sort(
      with(dat2, V1/sum(V1))
      )
    ), digits = 6)

length(
  which(
    round(cumsum(sort(with(dat2, V1/sum(V1)))), digits = 6) < 0.05)
  ) # 46 interviewer are on the left side below the lower 5 percent
```


Get the interviewer id and rowsums ordered the same way like the densities.
Get the number of interviews.

```{r}
sort.calc4$INTNUM1
sort.calc4$rowsum


```


## resample for single interviews


```{r}
N2 <- 100000; SP2 <- sample(
                      calc6$rowsum,
                      N2,
                      replace=T
                      ) # now sample the same resample for the separated interviews

mean(SP2) # 21768691
sd(SP2) # 15497107
# 21768691-15497107=6271584
# 21768691+15497107=37265798

mean(calc6$rowsum) # 21812202
sd(calc6$rowsum) # 15601634
# 21812202-15601634=6210568
# 21812202+15601634=37413836



plot(density(SP2),
     col ="grey",
     main = "Plausibilit채t",
     xlab= "Totalvariabilit채t T in Einzelinterviews (gepunktet MW +/- St.Abw.)",
     lwd=2); lines(density(calc6$rowsum),
                   col= "black",
                   lwd=2); abline(v= c(6271584, 21768691, 37265798),
                                  col="grey",
                                  lty="dotted",
                                  lwd=3); abline(v= c(6210568, 21812202, 37413836),
                                  col="black",
                                  lty="dotted",
                                  lwd=3); legend("topright", legend = c("SP", "Resample"),  fill = c("black", "grey"), bty = "n");
                                    options(scipen=5)

dat3 <- data.frame(V1 = calc6$rowsum)

round(
  sort(
    with(dat3, V1/sum(V1))
    ), digits = 6)

round(
  cumsum(
    sort(with(dat3, V1/sum(V1)))
    ), digits = 6)

length(
  which(
    round(cumsum(sort(with(dat3, V1/sum(V1)))), digits = 6) < 0.05)
  ) # 281 interviews are on the left side below the lower 5 percent
```


# qualitative evaluation


Get tidy data for clustering.
Write a csv and extract infos to get an overview of the ranking.

```{r}
getwd()

write.csv2(sort.calc6, "2sorted_ranking_calc6.csv",sep = ";")

sort(table(mergeddata$INTNUM1))
head(mergeddata, n = 5)

Intnum_count_each <- mergeddata[,-c(3:length(mergeddata))] %>% 
  rowwise %>% 
  mutate(time=list(rep(INTNUM1))) # repeat the INTNUM1 based on its counts

head(Intnum_count_each, n = 5)

length(unique(
  Intnum_count_each$INTNUM1)
  ) # 193 unique interviewers

Intnum_count_each2 <- Intnum_count_each %>% 
  group_by(INTNUM1) %>% 
  mutate(count = n()
         ) # put in a occurrence variable

head(Intnum_count_each2, n = 5)

Intnum_count_each3 <- Intnum_count_each2[, -c(3)] %>% 
  group_by(INTNUM1, count) %>%
  mutate(count = n()
         ) # grouping and erase irrelevant var

rm(list = c("Intnum_count_each", "Intnum_count_each2"))

head(Intnum_count_each3, n = 5)


rowsum_by_idno_intnum3 <- cbind.data.frame(calc6, Intnum_count_each3[,3])

write.csv2(rowsum_by_idno_intnum3, "data.csv")
getwd() 


hj <- rowsum_by_idno_intnum3[!duplicated(rowsum_by_idno_intnum3$INTNUM1), ]
write.csv2(hj, "data2.csv")



hj <- read.csv2("data2.csv", header=T)
hj <- hj[,-c(6:13)]
hj2 <- hj[,-c(1,3)]
```