---
title: "Variability"
author: "Kevin Glock"
date: "29 01 2021"
output:
  html_document:
    highlight: textmate
  toc_depth: 2
  number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
    echo = TRUE,
      include = TRUE,
    eval = TRUE,
  message = FALSE,
    results = 'hide',
      tidy = TRUE,
    tidy.opts = list(
      width.cutoff=60
      )
    )

#eval whether to evaluate the chunk
#echo whether to echo source code
#results 'markup', 'asis', 'hold', 'hide'
#tidy whether to reformat R code
#cache whether to cache results
#g.width, g.height, out.width, out.height device and output size of gures
#include whether to include the chunk results in output
#child lenames of child documents
#engine language name (R, python, . . . )
```


# variability approach


For the variability approach in the first step the variance for each interviewer and every question is calculated and summed up.
The difference between each observation for a question by interviewer and the mean of the question will provide a t-statistic which can be tested against a resampled distribution.

```{r}
dim(mergeddata)

anew <- subset.data.frame(mergeddata,
                          select = -c(3,5,7)) %>% 
  group_by(idno, INTNUM1) # sort it by interviewer and match each interview

head(anew) 

anew[is.na(anew)] <-0 # All NAs should be 0 because of calculations

dim(anew)
head(anew) # Now the data is tidy; 1685 obs on 557 var
```


## calculate the means


Pay attention for 1685 entries, 557 total columns but idno and INTNUM1-3 should not be includes.

```{r}
bnew <- anew[,c(5:557)] %>% 
  colMeans() %>% 
  rbind.data.frame()

names(bnew) <- colnames(anew[5:557])

head(bnew) # now we have the mean values for every variable

bnew <- bnew[rep(
  seq_len(
    ncol(bnew)
    ), 
  each = 1685), ] # each must be adapted

head(bnew, n = 5)
tail(bnew, n = 5)

bnew <- bnew[-c(1686:nrow(bnew)), ] # make sure there are no redundant rows

nrow(bnew) # 1685

# now we have a df with all means for every variable for each observation
# we have to apply the calculation for each observation

head(anew)

cnew <- anew[,-(1:4)] # we have to remove idno and INTNUM1-3 to make rowwise calculations in the next step

dim(cnew) # stated values for each interview; 1685 obs and 553 vars
dim(bnew) # mean for each question; 1685 obs and 553 vars

```


## calculate variabilities


Variability for each question over each interview

```{r}
calc <- (cnew-bnew)^2
head(calc)

calc2 <- cbind(
  anew[,c("idno","INTNUM1", "INTNUM2", "INTNUM3")], calc
  )

dim(calc2) # like before 1685 obs on 557 vars
head(calc2)

calc3 <- calc2 %>% 
  group_by(INTNUM1, INTNUM2, INTNUM3) %>% 
  summarise(.groups = "keep", 
            across(.cols = 5:554,
                   .fns = sum
                   )
            ) # sum up for each interviewer over all questions

rm(list = c("anew", "bnew", "cnew"))

dim(calc3) # 208 obs because of grouping by INTNUM1-3 and 553 vars
head(calc3)
```


## get the test statistic T


Get the test statistic T (total variability) for the clustered interviewer and for the whole survey.

```{r}
calc4 <- cbind.data.frame(
  calc3[c("INTNUM1", "INTNUM2", "INTNUM3")],
  rowsum = rowSums(calc3[4:553])
  ) # create a new object containing the INTNUMs and the total variability aggregated by INTNUMs

sort.calc4 <- calc4[order(calc4$rowsum) ,] # resort it by the rowsums to get ascending values of the variabilities

head(sort.calc4, n = 5) 

plot(density(calc4$rowsum)
     ); options(scipen=5) # the density of variability over all interviewers

sd(calc4$rowsum) # 119066864
mean(calc4$rowsum) # 176699700

sort(table(calc4$INTNUM1)
     ) # we can see that some are double or triple this is because they are re-issued by a second and third person
head(calc4, n = 20) # look on the entries 6 and 7 for example

length(which(sort.calc4$rowsum < 100000000)) # fifty-seven interviews show suspiciously low total variabilities at first sight

head(sort.calc4, n = 5) # lowest value 6044290 for interviewer 2086; keep in mind that this are aggregated values!
tail(sort.calc4, n = 5) # highest value 599664843 for interviewer 6049
```


## whole dataset


Get independent variabilities for the interviews.

```{r}
calc5 <- cbind(
  calc2[c("idno", "INTNUM1")], calc
  ); head(calc5, n = 5)

calc6 <- cbind.data.frame(
  calc5[c("idno", "INTNUM1")], 
  rowsum=rowSums(calc5[3:554])
  ); head(calc6, n = 5)

plot(density(calc6$rowsum)
     ) # density plot for unique interviews not grouped by interviewers

sd(calc6$rowsum) # 15601634
mean(calc6$rowsum) #21812202

sort.calc6 <- calc6[order(calc6$rowsum) ,] # now sorted by rowsums not by respondends ID

head(sort.calc6, n = 5) # lowest value 2352503 for interview 2308; keep in mind that this are seperated interview values not aggregated
tail(sort.calc6, n = 5) # highest value 104602583 for interview 2089
```
