---
title: "Clustering"
author: "Kevin Glock"
date: "28 01 2021"
output:
  html_document:
    highlight: textmate
  toc_depth: 2
  number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
    echo = TRUE,
      include = TRUE,
    eval = TRUE,
  message = FALSE,
    results = 'hide',
      tidy = TRUE,
    tidy.opts = list(
      width.cutoff=60
      )
    )

#eval whether to evaluate the chunk
#echo whether to echo source code
#results 'markup', 'asis', 'hold', 'hide'
#tidy whether to reformat R code
#cache whether to cache results
#g.width, g.height, out.width, out.height device and output size of gures
#include whether to include the chunk results in output
#child lenames of child documents
#engine language name (R, python, . . . )
```

# clustering first step


Get tidy data for clustering.
Write a csv and extract infos to get an overview of the ranking.

```{r}
getwd()

write.csv2(sort.calc6, "2sorted_ranking_calc6.csv",sep = ";")

sort(table(mergeddata$INTNUM1))
head(mergeddata, n = 5)

Intnum_count_each <- mergeddata[,-c(3:length(mergeddata))] %>% 
  rowwise %>% 
  mutate(time=list(rep(INTNUM1))) # repeat the INTNUM1 based on its counts

head(Intnum_count_each, n = 5)

length(unique(
  Intnum_count_each$INTNUM1)
  ) # 193 unique interviewers

Intnum_count_each2 <- Intnum_count_each %>% 
  group_by(INTNUM1) %>% 
  mutate(count = n()
         ) # put in a occurrence variable

head(Intnum_count_each2, n = 5)

Intnum_count <- Intnum_count_each2[, -c(3)] %>% 
  group_by(INTNUM1, count) %>%
  mutate(count = n()
         ) # grouping and erase irrelevant var

rm(list = c("Intnum_count_each", "Intnum_count_each2"))

head(Intnum_count_each3, n = 5)
```


## clustering second step


Create a new object containing the counts.

```{r}
rowsum_by_idno_intnum <- calc6 %>% 
  group_by(INTNUM1) %>% 
  mutate(count = n()
         ); head(rowsum_by_idno_intnum, n = 5)

rowsum_by_idno_intnum2 <- rowsum_by_idno_intnum[, -c(2, 4)] # one dataset with only the idno and rowsum
head(rowsum_by_idno_intnum2, n = 5)
```


Create new subsets based on the number of interviews an interviewer had to compare them within the groups.

```{r}

o1 <- rowsum_by_idno_intnum %>% 
  subset(count==1); o1 <- o1[,-4]

o1 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o1)

o2 <- rowsum_by_idno_intnum %>% 
  subset(count== 2); o2 <- o2[,-4]

o2 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o2)

o3 <- rowsum_by_idno_intnum %>% 
  subset(count== 3); o3 <- o3[,-4]

o3 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o3)

o4 <- rowsum_by_idno_intnum %>% 
  subset(count==4); o4 <- o4[,-4]

o4 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o4)

o5 <- rowsum_by_idno_intnum %>% 
  subset(count==5); o5 <- o5[,-4]

o5 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o5)

o6 <- rowsum_by_idno_intnum %>% 
  subset(count==6); o6 <- o6[,-4]

o6 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o6)

o7 <- rowsum_by_idno_intnum %>% 
  subset(count==7); o7 <- o7[,-4]

o7 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o7)

o8 <- rowsum_by_idno_intnum %>% 
  subset(count==8); o8 <-  o8[,-4]

o8 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o8)

o9 <- rowsum_by_idno_intnum %>% 
  subset(count==9); o9 <- o9[,-4]

o9 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o9)

o10 <- rowsum_by_idno_intnum %>% 
  subset(count==10); o10 <- o10[,-4]

o10 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o10)

o11 <- rowsum_by_idno_intnum %>% 
  subset(count==11); o11 <- o11[,-4]

o11 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o11)

o12 <- rowsum_by_idno_intnum %>% 
  subset(count==12); o12 <- o12[,-4]

o12 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o12)

o13 <- rowsum_by_idno_intnum %>% 
  subset(count==13); o13 <- o13[,-4]

o13 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o13)

o14 <- rowsum_by_idno_intnum %>% 
  subset(count==14); o14 <- o14[,-4]

o14 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o14)

o15 <- rowsum_by_idno_intnum %>% 
  subset(count==15); o15 <- o15[,-4]

o15 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o15)

o17 <- rowsum_by_idno_intnum %>% 
  subset(count==17); o17 <- o17[,-4]

o17 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o17)

o18 <- rowsum_by_idno_intnum %>% 
  subset(count==18); o18 <- o18[,-4]

o18 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o18)

o20 <- rowsum_by_idno_intnum %>% 
  subset(count==20); o20 <- o20[,-4]

o20 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o20)

o21 <- rowsum_by_idno_intnum %>% 
  subset(count==21); o21 <- o21[,-4]

o21 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o21)

o22 <- rowsum_by_idno_intnum %>% 
  subset(count==22); o22 <- o22[,-4]

o22 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o22)

o27 <- rowsum_by_idno_intnum %>% 
  subset(count==27); o27 <- o27[,-4]

o27 %>% mutate_each_(funs(scale), vars=c("rowsum"))
#head(o27)
```


# clustering third step


Create distant matrices.

```{r}
## with all interviews

dist.fun0 <-dist(rowsum_by_idno_intnum, method="euclidean")


## only with one interview

dist.fun1 <-dist(o1, method="euclidean")


## only with two interviews

dist.fun2 <-dist(o2, method="euclidean")


## only with three interviews

dist.fun3 <-dist(o3, method="euclidean")


## only with four interviews

dist.fun4 <-dist(o4, method="euclidean")


## only with five interviews

dist.fun5 <-dist(o5, method="euclidean")


## only with six interviews

dist.fun6 <-dist(o6, method="euclidean")


## only with seven interviews

dist.fun7 <-dist(o7, method="euclidean")


## only with eight interviews

dist.fun8 <-dist(o8, method="euclidean")


## only with nine interviews

dist.fun9 <-dist(o9, method="euclidean")


## only with ten interviews

dist.fun10 <-dist(o10, method="euclidean")


## only with eleven interviews

dist.fun11 <-dist(o11, method="euclidean")


## only with twelve interviews

dist.fun12 <-dist(o12, method="euclidean")


## only with thirteen interviews

dist.fun13 <-dist(o13, method="euclidean")


## only with fourteen interviews

dist.fun14 <-dist(o14, method="euclidean")


## only with fifteen interviews

dist.fun15 <-dist(o15, method="euclidean")


## only with seventeen interviews

dist.fun17 <-dist(o17, method="euclidean")


## only with eighteen interviews

dist.fun18 <-dist(o18, method="euclidean")


## only with twenty interviews

dist.fun20 <-dist(o20, method="euclidean")


## only with twenty-one interviews

dist.fun21 <-dist(o21, method="euclidean")


## only with twenty-two interviews

dist.fun22 <-dist(o22, method="euclidean")


## only with twenty-seven interviews

dist.fun27 <-dist(o27, method="euclidean")
```


# clustering last step


Create hierarical clusters.

```{r}
## overall

fit.0 <-hclust(dist.fun0, method = "single")

fit0.2 <-hclust(dist.fun0, method = "ward.D2")


## only with one interview

fit.1 <-hclust(dist.fun1, method = "single")

fit1.2 <-hclust(dist.fun1, method = "ward.D2")


## only with two interviews

fit.2 <-hclust(dist.fun2, method = "single")

fit2.2 <-hclust(dist.fun2, method = "ward.D2")


## only with three interviews

fit.3 <-hclust(dist.fun3, method = "single")

fit3.2 <-hclust(dist.fun3, method = "ward.D2")


## only with four interviews

fit.4 <-hclust(dist.fun4, method = "single")

fit4.2 <-hclust(dist.fun4, method = "ward.D2")


## only with five interviews

fit.5 <-hclust(dist.fun5, method = "single")

fit5.2 <-hclust(dist.fun5, method = "ward.D2")


## only with six interviews

fit.6 <-hclust(dist.fun6, method = "single")

fit6.2 <-hclust(dist.fun6, method = "ward.D2")


## only with seven interviews

fit.7 <-hclust(dist.fun7, method = "single")

fit7.2 <-hclust(dist.fun7, method = "ward.D2")


## only with eight interviews

fit.8 <-hclust(dist.fun8, method = "single")

fit8.2 <-hclust(dist.fun8, method = "ward.D2")


## only with nine interviews

fit.9 <-hclust(dist.fun9, method = "single")

fit9.2 <-hclust(dist.fun9, method = "ward.D2")


## only with ten interviews

fit.10 <-hclust(dist.fun10, method = "single")

fit10.2 <-hclust(dist.fun10, method = "ward.D2")


## only with eleven interviews

fit.11 <-hclust(dist.fun11, method = "single")

fit11.2 <-hclust(dist.fun11, method = "ward.D2")


## only with twelve interviews

fit.12 <-hclust(dist.fun12, method = "single")

fit12.2 <-hclust(dist.fun12, method = "ward.D2")


## only with thirteen interviews

fit.13 <-hclust(dist.fun13, method = "single")

fit13.2 <-hclust(dist.fun13, method = "ward.D2")


## only with fourteen interviews

fit.14 <-hclust(dist.fun14, method = "single")

fit14.2 <-hclust(dist.fun14, method = "ward.D2")


## only with fifteen interviews

fit.15 <-hclust(dist.fun15, method = "single")

fit15.2 <-hclust(dist.fun15, method = "ward.D2")


## only with seventeen interviews

fit.17 <-hclust(dist.fun17, method = "single")

fit17.2 <-hclust(dist.fun17, method = "ward.D2")


## only with eighteen interviews

fit.18 <-hclust(dist.fun18, method = "single")

fit18.2 <-hclust(dist.fun18, method = "ward.D2")


## only with twenty interviews

fit.20 <-hclust(dist.fun20, method = "single")

fit20.2 <-hclust(dist.fun20, method = "ward.D2")


## only with twenty-one interviews

fit.21 <-hclust(dist.fun21, method = "single")

fit21.2 <-hclust(dist.fun21, method = "ward.D2")


## only with twenty-two interviews

fit.22 <-hclust(dist.fun22, method = "single")

fit22.2 <-hclust(dist.fun22, method = "ward.D2")


## only with twenty-seven interviews

fit.27 <-hclust(dist.fun27, method = "single")

fit27.2 <-hclust(dist.fun27, method = "ward.D2")
```


# Dendrograms


```{r}
#Dendograms

plot(fit.0, labels=rowsum_by_idno_intnum$INTNUM1, cex=0.6); options(scipen = 5)
plot(fit0.2, labels=rowsum_by_idno_intnum$INTNUM1, cex=0.6); options(scipen = 5)

plot(fit.1, labels=o1$idno, cex=0.6); options(scipen = 5)
plot(fit1.2, labels=o1$idno, cex=0.6); options(scipen = 5)

plot(fit.2, labels=o2$idno, cex=0.6); options(scipen = 5)
plot(fit2.2, labels=o2$idno, cex=0.6); options(scipen = 5)

plot(fit.3, labels=o3$idno, cex=0.6); options(scipen = 5)
plot(fit3.2, labels=o3$idno, cex=0.6); options(scipen = 5)

plot(fit.4, labels=o4$idno, cex=0.6); options(scipen = 5)
plot(fit4.2, labels=o4$idno, cex=0.6); options(scipen = 5)

plot(fit.5, labels=o5$idno, cex=0.6); options(scipen = 5)
plot(fit5.2, labels=o5$idno, cex=0.6); options(scipen = 5)

plot(fit.6, labels=o6$idno, cex=0.6); options(scipen = 5)
plot(fit6.2, labels=o6$idno, cex=0.6); options(scipen = 5)

plot(fit.7, labels=o7$idno, cex=0.6); options(scipen = 5)
plot(fit7.2, labels=o7$idno, cex=0.6); options(scipen = 5)

plot(fit.8, labels=o8$idno, cex=0.6); options(scipen = 5)
plot(fit8.2, labels=o8$idno, cex=0.6); options(scipen = 5)

plot(fit.9, labels=o9$idno, cex=0.6); options(scipen = 5)
plot(fit9.2, labels=o9$idno, cex=0.6); options(scipen = 5)

plot(fit.10, labels=o10$idno, cex=0.6); options(scipen = 5)
plot(fit10.2, labels=o10$idno, cex=0.6); options(scipen = 5)

plot(fit.11, labels=o11$idno, cex=0.6); options(scipen = 5)
plot(fit11.2, labels=o11$idno, cex=0.6); options(scipen = 5)

plot(fit.12, labels=o12$idno, cex=0.6); options(scipen = 5)
plot(fit12.2, labels=o12$idno, cex=0.6); options(scipen = 5)

plot(fit.13, labels=o13$idno, cex=0.6); options(scipen = 5)
plot(fit13.2, labels=o13$idno, cex=0.6); options(scipen = 5)

plot(fit.14, labels=o14$idno, cex=0.6); options(scipen = 5)
plot(fit14.2, labels=o14$idno, cex=0.6); options(scipen = 5)

plot(fit.15, labels=o15$idno, cex=0.6); options(scipen = 5)
plot(fit15.2, labels=o15$idno, cex=0.6); options(scipen = 5)

plot(fit.17, labels=o17$idno, cex=0.6); options(scipen = 5)
plot(fit17.2, labels=o17$idno, cex=0.6); options(scipen = 5)

plot(fit.18, labels=o18$idno, cex=0.6); options(scipen = 5)
plot(fit18.2, labels=o18$idno, cex=0.6); options(scipen = 5)

plot(fit.20, labels=o20$idno, cex=0.6); options(scipen = 5)
plot(fit20.2, labels=o20$idno, cex=0.6); options(scipen = 5)

plot(fit.21, labels=o21$idno, cex=0.6); options(scipen = 5)
plot(fit21.2, labels=o21$idno, cex=0.6); options(scipen = 5)

plot(fit.22, labels=o22$idno, cex=0.6); options(scipen = 5)
plot(fit22.2, labels=o22$idno, cex=0.6); options(scipen = 5)

plot(fit.27, labels=o27$idno, cex=0.6); options(scipen = 5)
plot(fit27.2, labels=o27$idno, cex=0.6); options(scipen = 5)
```


# get density plots per subgroup


```{r}

plot(density(rowsum_by_idno_intnum$rowsum)); options(scipen = 5)

plot(density(o1$rowsum)); options(scipen = 5)

plot(density(o2$rowsum)); options(scipen = 5)

plot(density(o3$rowsum)); options(scipen = 5)

plot(density(o4$rowsum)); options(scipen = 5)

plot(density(o5$rowsum)); options(scipen = 5)

plot(density(o6$rowsum)); options(scipen = 5)

plot(density(o7$rowsum)); options(scipen = 5)

plot(density(o8$rowsum)); options(scipen = 5)

plot(density(o9$rowsum)); options(scipen = 5)

plot(density(o10$rowsum)); options(scipen = 5)

plot(density(o11$rowsum)); options(scipen = 5)

plot(density(o12$rowsum)); options(scipen = 5)

plot(density(o13$rowsum)); options(scipen = 5)

plot(density(o13$rowsum)); options(scipen = 5)

plot(density(o14$rowsum)); options(scipen = 5)

plot(density(o15$rowsum)); options(scipen = 5)

plot(density(o17$rowsum)); options(scipen = 5)

plot(density(o18$rowsum)); options(scipen = 5)

plot(density(o20$rowsum)); options(scipen = 5)

plot(density(o21$rowsum)); options(scipen = 5)

plot(density(o22$rowsum)); options(scipen = 5)

plot(density(o27$rowsum)); options(scipen = 5)
```

